\section{Introduction}
\label{sec:introduction}
\IEEEPARstart{R}{espiratory} diseases remain a major public health burden across all age groups, with chronic obstructive pulmonary disease (COPD) among the most severe and prevalent conditions. COPD is characterized by persistent airway inflammation and airflow limitation and is often associated with breathlessness, wheezing, crackles, rhonchi, and, in advanced cases, respiratory failure~\cite{b01}. Since abnormal respiratory sounds carry clinically meaningful information about airway obstruction and pulmonary function, automated lung sound analysis offers a non-invasive route for early screening and clinical decision support. The characteristics of pathological respiratory sounds are summarized in Table~\ref{tab:resp_chars}.

Global burden studies indicate that COPD remains a leading cause of mortality worldwide~\cite{b02,b03}. However, many cases remain underdiagnosed because respiratory symptoms are often ignored until disease progression becomes clinically severe. This motivates the development of accessible diagnostic systems that can operate close to the patient, support timely screening, and reduce dependence on centralized computing infrastructure.

Machine learning and deep learning methods have been widely investigated for respiratory sound classification, including handcrafted acoustic features, spectrogram-based convolutional models, recurrent networks, and transformer-based architectures~\cite{b07,b08,b09,b10,b11,b12,b13,b14,b15}. Although these methods have improved diagnostic accuracy, most existing pipelines are evaluated as static offline classifiers in which every sample is processed by the same model regardless of diagnostic difficulty. Such a design is inefficient for edge deployment, where many respiratory segments can be classified confidently using lightweight features, while only ambiguous cases require computationally intensive spatial-spectral analysis.

This limitation exposes an important research gap. Prior respiratory sound classification studies primarily optimize classification performance, but fewer studies jointly address uncertainty-aware inference, low-power edge execution, and hardware--software co-design on heterogeneous FPGA platforms. Portable digital stethoscopes and wearable monitoring devices require low latency, limited memory usage, energy efficiency, and local processing for privacy-preserving operation. Therefore, diagnostic accuracy alone is insufficient; the inference pipeline must also adapt its computational cost to the complexity of each input sample.

\input{tables/table_1.tex}

To address this gap, this study proposes an \textit{Uncertainty-Aware Heterogeneous Cascaded Inference} (UA-HCI) framework for respiratory sound analysis on FPGA-based edge devices. The framework uses lightweight one-dimensional statistical features and Random Forest classifiers for early-exit screening on the ARM Processing System, while uncertain samples are routed to a hybrid spectrogram representation and processed by a MobileNetV2 student model on the Programmable Logic through the Xilinx DPU. By combining uncertainty-aware routing with quantization-aware training (QAT) and hardware--software co-design, the proposed system reduces unnecessary deep neural inference while preserving diagnostic performance.

The main contributions of this work are summarized as follows:
\begin{itemize}
    \item We propose the UA-HCI framework, a dynamic cascaded diagnostic pipeline that uses Random Forest-based early-exit decisions for confident respiratory samples and reserves CNN-based spatial-spectral classification for uncertain cases.
    \item We develop a heterogeneous FPGA deployment strategy that maps control-oriented screening stages to the ARM Processing System and the INT8-quantized MobileNetV2 stage to the Programmable Logic using PYNQ, Vitis AI, and the Xilinx DPU.
    \item We validate the framework on a merged ICBHI and KAUH respiratory sound dataset under subject-independent evaluation, achieving 96.56\% best-fold accuracy and 94.94\% mean accuracy across three diagnostic categories (Healthy, COPD, and Non-COPD), and define route-level measurements for quantifying energy savings compared with a static CNN deployment.
\end{itemize}

The remainder of this paper is organized as follows. Section~\ref{sec:relatedwork} reviews prior studies on respiratory sound classification. Section~\ref{sec:methodology} describes the proposed cascaded inference framework, feature extraction pipeline, and FPGA-oriented hardware-software partitioning. Section~\ref{sec:experimentsResults} presents the experimental validation, quantization results, and hardware performance analysis. Finally, Section~\ref{sec:conclusion} concludes the paper.
