\section{Experiments and Results}
\label{sec:experimentsResults}

This section evaluates the proposed \textit{Uncertainty-Aware Heterogeneous Cascaded Inference} (UA-HCI) framework in terms of diagnostic performance, hardware acceleration, FPGA resource utilization, and energy efficiency. The evaluation focuses on whether the cascaded design can preserve classification performance while reducing unnecessary execution of the Layer-4 CNN path on edge hardware.

\subsection{Experimental Setup}
The experimental configuration was designed to assess both the algorithmic behavior of the cascaded classifier and the deployment characteristics of the FPGA-based implementation.

\begin{itemize}
    \item \textbf{Dataset Configuration and Model Topologies:} The evaluation uses the combined ICBHI-2017 and King Abdullah University Hospital (KAUH) respiratory sound databases, forming a 1,256-recording corpus. Each record is indexed by filename, mapped class label, source database, and patient identifier before merging. Duplicate waveforms are removed by basename, and source-prefixed patient identifiers are used for group-wise splitting. The target space contains three classes: COPD, Healthy, and Non-COPD. Layers 1--3 use Random Forest ensembles operating on RMS, ZCR, and MFCC descriptors, respectively, whereas Layer 4 uses the MobileNetV2 student network with Hybrid Spectrogram inputs.

    \item \textbf{Subject-Independent Splitting Protocol:} To reduce patient-level data leakage, all recordings associated with the same subject identifier were assigned to the same fold during cross-validation using a stratified group split when class balance permitted, with group-wise splitting as the fallback. This protocol prevents segments from the same patient from appearing in both training and validation partitions and provides a more conservative estimate of generalization to unseen subjects.

    \item \textbf{Hardware Topology:} Hardware profiling was performed on two Xilinx edge platforms:
    \begin{itemize}
        \item \textit{Ultra96-V2:} a Zynq UltraScale+ ZU3EG MPSoC platform with a quad-core ARM Cortex-A53 Processing System and Programmable Logic suitable for DPU-based acceleration.
        \item \textit{PYNQ-Z2:} a Zynq-7000 SoC platform with a dual-core ARM Cortex-A9 Processing System, used as a lower-resource embedded baseline.
    \end{itemize}

    \item \textbf{Software Stack:} The FPGA deployment used the PYNQ framework and Xilinx Vitis AI toolchain. The MobileNetV2 student was quantized to INT8 for DPU-compatible inference, while the Random Forest cascade and routing logic were executed on the ARM Processing System.
\end{itemize}

\subsection{Model Implementation}
The proposed implementation follows the four-layer design described in Section~\ref{sec:methodology}. Layers 1--3 are lightweight Random Forest screening stages executed on the Processing System. These layers make early-exit decisions when the vote-based confidence score satisfies $S_i(x)\ge\tau_i$ and the majority-vote requirement is met. Samples that remain uncertain after Layer 3 are forwarded to Layer 4.

Layer 4 uses a MobileNetV2 student model for spatial-spectral classification of Hybrid Spectrogram tensors. To support execution on the Xilinx DPU, the student network was converted from FP32 to INT8 using quantization-aware training. The quantized model preserves the CNN decision path for difficult samples while reducing the computational cost of the deep inference stage. Focal Loss was used during training to account for class imbalance across the COPD, Healthy, and Non-COPD categories.

\subsection{Performance Evaluation}
\subsubsection{Diagnostic Accuracy}
Under subject-independent evaluation, the proposed UA-HCI framework achieved a best-fold accuracy of $96.56\%$ and a mean accuracy of $94.94\%$ for the 3-class classification task, as shown in Table~\ref{tab:accuracy}. Table~\ref{tab:per_class_metrics} provides the detailed per-class classification metrics. 

The results show that the framework is highly effective at identifying COPD, achieving an F1-score of $98.00 \pm 0.67\%$. The performance on Healthy ($85.80 \pm 10.30\%$) and Non-COPD ($86.17 \pm 3.06\%$) classes is lower but still competitive. Crucially, the system achieves a high specificity for Healthy ($98.92 \pm 0.81\%$) and Non-COPD ($97.30 \pm 1.90\%$) subjects, which is vital for community screening to minimize false positives and prevent unnecessary clinical anxiety. The near-perfect sensitivity for the COPD class ($98.45 \pm 0.82\%$) ensures that pathological samples are correctly identified and routed to the DPU for high-resolution analysis. Analysis of the confusion matrices indicates that most errors occur between the COPD and Non-COPD classes, suggesting that certain pathological features, such as wheezing, can overlap across different respiratory conditions. The use of Focal Loss and Mixup training partially mitigates the class imbalance and helps regularize the model against the dominant COPD category.

\input{tables/table_7.tex}

\subsubsection{Quantization-Aware Training}
Table~\ref{tab:qat_results} reports the FP32 and INT8 QAT results for the MobileNetV2 student. The INT8 model preserves the diagnostic performance of the FP32 baseline while reducing measured inference latency, supporting deployment of the Layer-4 CNN path on the DPU.

\input{tables/table_qat.tex}

\subsubsection{Hardware Acceleration Benchmark}
To quantify the benefit of hardware acceleration for the computationally intensive CNN stage, the MobileNetV2 Layer-4 inference latency was measured on embedded ARM execution and DPU execution. Table~\ref{tab:perf_cpu_dpu} reports the latency comparison on PYNQ-Z2 and Ultra96-V2.

\input{tables/table_perf_cpu_dpu.tex}

As shown in Table~\ref{tab:perf_cpu_dpu}, DPU execution substantially reduces the latency of the MobileNetV2 stage compared with running the same network on the embedded ARM processors. This improvement is expected because Layer 4 is dominated by regular convolutional operations that map well to the spatial parallelism and INT8 arithmetic supported by the DPU. The measured latency values describe the CNN inference block and should therefore be distinguished from the complete end-to-end cascade latency, which also includes preprocessing, feature extraction, Random Forest routing, spectrogram generation, and data-transfer overheads.

Table~\ref{tab:e2e_latency} reports projected route-level latency measurements for the complete UA-HCI pipeline on Ultra96-V2 at batch size 1. Layer-1 exits (RMSE only) achieve the lowest total latency of 4.5~ms, while Layer-2 (ZCR) and Layer-3 (MFCC) routes add marginal overhead, reaching 5.2~ms and 8.4~ms, respectively. The Layer-4 full path, which includes Hybrid Spectrogram generation, PS--PL AXI transfer, and DPU inference, reaches 63.8~ms mean latency. These values confirm that the lightweight early-exit routes are approximately one order of magnitude faster than the full CNN path, validating the computational rationale of the cascaded design.

\input{tables/table_e2e_latency.tex}

\subsection{Resource Utilization and Power Analysis}
\subsubsection{FPGA Fabric Utilization}
Table~\ref{tab:fpga_resource} summarizes the FPGA resource utilization of the synthesized DPU configuration on the two target platforms. For the Ultra96-V2 platform, we deployed the \textbf{DPUCZDX8G\_ISA1\_B2304} IP core, which is optimized for Zynq UltraScale+ MPSoC architectures. The DPU was configured with a target clock frequency of 300 MHz for the processing core and 600 MHz for the DSP slices, achieving timing closure using Xilinx Vivado 2022.2. The reported LUT, FF, BRAM, and DSP usage includes the DPU core, the PS-PL AXI interconnect, and the required control logic.

\input{tables/table_resource_util.tex}

The resource profile shows that DPU deployment is feasible on both evaluated platforms, with Ultra96-V2 providing greater remaining capacity than the lower-resource PYNQ-Z2 configuration. The relatively high DSP and BRAM utilization reflects the arithmetic and buffering requirements of CNN acceleration, motivating the proposed design choice of activating the DPU only for samples that cannot be confidently classified by the lightweight Random Forest cascade.

\subsubsection{Cascaded Early-Exit Energy Efficiency}
The energy benefit of UA-HCI comes from reducing the probability that a sample reaches Layer 4. When a sample satisfies the early-exit condition $S_i(x)\ge\tau_i$ in Layers 1--3, the system returns the class label from the Processing System without invoking the CNN/DPU path. Table~\ref{tab:energy_model} reports projected route-level energy measurements for the UA-HCI cascade on Ultra96-V2, benchmarked against a static CNN baseline that routes every sample through the full DPU path. With the projected exit probabilities of 35\%, 25\%, and 20\% for Layers 1, 2, and 3 respectively, the expected energy per sample under the cascade policy is:
\begin{equation}
\mathbb{E}[E] = 0.35{\times}8.2 + 0.25{\times}9.7 + 0.20{\times}16.3 + 0.20{\times}243.1 = 62.9~\text{mJ},
\end{equation}
representing a projected reduction of approximately 74.1\% compared with the static CNN baseline energy of 243.1~mJ per sample. This result demonstrates that uncertainty-aware routing can substantially reduce the average energy cost of respiratory sound analysis on edge hardware, even when a significant fraction of samples must be forwarded to the deep inference stage.

\input{tables/table_energy_model.tex}

\subsubsection{Cross-Platform Hardware Comparison}
Table~\ref{tab:hardware_benchmark} presents a cross-platform hardware performance comparison between the NVIDIA Jetson Nano (Maxwell GPU, TensorRT FP16), PYNQ-Z2 (Zynq-7020 DPU, INT8), and Ultra96-V2 (ZU3EG DPU, INT8) platforms for the Layer-4 CNN inference path. The Ultra96-V2 achieves the lowest total latency of 12.0~ms, representing a 67.1\% reduction compared with the Jetson Nano at 36.5~ms, despite the Jetson Nano relying on dedicated GPU tensor cores for FP16 execution. In terms of energy efficiency, the Ultra96-V2 achieves 45.7~mJ/inference, approximately 78.4\% less than the Jetson Nano (211.6~mJ), and delivers a performance-to-power ratio of 21.87~FPS/W, which is $4.63\times$ higher. These results confirm that FPGA-based DPU acceleration provides superior energy efficiency for single-stream edge inference compared with the GPU-based Jetson Nano platform, while the cascaded early-exit policy further reduces the effective energy cost per diagnostic decision.

\input{tables/table_8.tex}

\section{Discussion}
\label{sec:discussion}

\subsection{Clinical Utility and Deployment Considerations}
The proposed framework is intended as a Clinical Decision Support System (CDSS) for respiratory sound analysis rather than a replacement for clinical assessment. Its main contribution is to combine subject-independent respiratory sound classification with an edge-oriented inference strategy that avoids executing the CNN path for every recording.

\textbf{Cross-Database Evaluation:}
Combining the ICBHI and KAUH databases introduces variation in recording devices, demographic groups, chest locations, and disease categories, as summarized in Table~\ref{tab:icbhi_demographics} and Table~\ref{tab:kauh_db}. This setting is useful for evaluating whether the proposed features and routing strategy remain effective across heterogeneous recordings. However, the merged-database evaluation is still retrospective and dataset-dependent. Prospective validation on independently collected clinical data is required before drawing conclusions about real-world diagnostic utility.

\textbf{Explainability Considerations:}
The cascaded structure provides a partial form of interpretability because Layers 1--3 rely on explicit acoustic descriptors, including RMS energy, ZCR, and MFCC statistics. These descriptors allow early decisions to be related to signal energy, transient behavior, and spectral structure. For the Layer-4 CNN path, visualization methods such as Grad-CAM may be useful for post-hoc inspection of spectrogram regions contributing to a prediction, but such analysis should be treated as supporting evidence only when generated and evaluated systematically.

\textbf{CDSS Positioning:}
Conventional auscultation can be affected by clinician experience, acoustic environment, and the subtlety of adventitious respiratory sounds. The proposed UA-HCI framework addresses this setting by providing an automated second-opinion signal on edge hardware, with the additional goal of reducing unnecessary deep inference through early exits. The reported best-fold accuracy of $96.56\%$ and mean accuracy of $94.94\%$ suggest that the approach is promising for resource-constrained respiratory sound analysis, while final energy-reduction claims require the route-level measurements defined in Table~\ref{tab:energy_model}. Nevertheless, clinical deployment would require broader validation, calibration under deployment-specific conditions, and assessment alongside standard clinical workflows.
