\section{Conclusion}
\label{sec:conclusion}
This study developed a hierarchical embedded system that uses respiratory sound features to diagnose respiratory diseases. The system was deployed on the Ultra96-V2 FPGA and achieved the expected accuracy and performance. With a mean accuracy of 94.94\% across three-fold cross-validation for three classes---Healthy, COPD, and Non-COPD---the model demonstrates the effectiveness of the proposed method for classifying respiratory conditions. The QAT evaluation showed a marginal accuracy change from 97.98\% to 97.47\% for the MobileNetV2 stage, while the hardware benchmark demonstrated that the Ultra96-V2 DPU achieves 8.2~ms Layer-4 inference latency, representing a 92.7\% reduction compared with embedded ARM execution (112.8~ms) on the same platform.

The system uses FPGA parallelism to reduce disease-classification time. Projected route-level latency measurements indicate that Layer-1, Layer-2, and Layer-3 early exits operate at 4.5~ms, 5.2~ms, and 8.4~ms respectively, approximately one order of magnitude below the 63.8~ms full Layer-4 path. With projected exit probabilities of 35\%, 25\%, and 20\% for the three early-exit routes, the expected energy per sample under the cascade policy is estimated at 62.9~mJ, representing a 74.1\% reduction compared with a static CNN baseline. Cross-platform comparison shows the Ultra96-V2 achieves 78.4\% lower energy per inference than the Jetson Nano and $4.63\times$ higher performance-per-watt, supporting deployment on mobile or embedded devices and potential use in clinical settings. The results suggest that uncertainty-aware routing is a promising direction for respiratory sound analysis on resource-constrained FPGA platforms. Future work should validate these projected route-level latency and energy measurements through physical hardware profiling, calibrate early-exit thresholds using prospective clinical recordings, and quantify the statistical stability of subject-independent evaluation across broader datasets, which may further support clinical diagnostic workflows and improve patient care.

\section*{Data Availability}
The ICBHI 2017 Respiratory Sound Database and the King Abdullah University Hospital Database used in this study are publicly available.
