\section{Introduction}
\label{sec:introduction}
\IEEEPARstart{R}{espiratory} diseases are a significant public health concern, affecting all age groups and causing considerable mortality rates. This group includes common illnesses such as upper respiratory tract infections (URTI), bronchitis, pneumonia, asthma, and Chronic Obstructive Pulmonary Disease (COPD). COPD is a severe condition characterized by chronic inflammation of the airway mucosa, leading to reduced pulmonary ventilation function. The main feature of COPD is airway narrowing, which causes breathlessness and potentially leads to respiratory failure (Singh et al., 2019) \cite{b01}. Common signs and symptoms include a persistent cough, chest pain, shortness of breath, difficulty breathing, wheezing, crackles, and rhonchi. The characteristics of pathological respiratory sounds are listed and compared in Table \ref{tab1}. Early diagnosis of respiratory diseases is crucial for timely intervention, slowing disease progression, and avoiding severe complications.

According to the World Health Organization (WHO) (Hashemi et al., 2020) \cite{b02}, COPD is projected to become the third leading cause of death globally by 2030. COPD is one of the most prevalent conditions in hospitals in respiratory wards(Mathers \& Loncar, 2006 \cite{b03}; Menzin et al., 2008 \cite{b04}; Yeatts et al., 2013 \cite{b05}). However, the actual prevalence may be much higher than reported, as many individuals do not undergo regular health check-ups and may ignore symptoms, thereby avoiding medical consultation.

Machine Learning has become a crucial tool in various fields and is increasingly influential in clinical medicine. Unlike traditional regression models, machine learning can assess various measurements of different types and account for nonlinear, higher-order interactions between independent variables. This capability enables the resolution of complex problems. For instance, machine learning methods have been utilized to predict the clinical progression of asthma and COPD exacerbations following emergency department triage, using routinely available triage data as predictors.

Deploying a real-time medical image processing system or module on personal computers often faces challenges related to performance and resources. Utilizing FPGA (Field-Programmable Gate Array) (Farooq et al., 2012) \cite{b06} and other specialized hardware, such as filters, ADCs, and wearable sensors, can provide a more effective solution for implementing medical image processing systems in practical environments. FPGA offers parallel processing capabilities and flexible configuration, allowing for performance optimization and latency reduction in real-time applications. This presents significant potential for applying FPGA advancements in medical diagnostics, where speed and accuracy are critical factors.

\input{tables/table_1.tex}

This research's main contribution included the following:
\begin{itemize}
    \item A proposed hierarchical embedded system using Random Forest and Lightweight CNN models with four resilient layers that achieve 98,81\% accuracy reach state-of-the-art results compared to other basic Machine Learning methods. Moreover, unlike previous methods that used static models, fixed parameters, and set-up conditions, this dynamic embedded system with high flexibility could complete the classification without completing four stages. It could be modified to adapt to various conditions of the dataset.
    \item Implement the proposed model on soft-hard system FPGA Ultra96V2 using PYNQ and Vitis-AI framework that works in real-time conditions and achieves impressive 52.5\% power saving and outperformance with excellent GOPs compared to traditional CPU-GPU methods.
    \item Conducted comprehensive experimental validation, including layer-specific performance analysis and comparison with state-of-the-art methods. The experiments demonstrated superior classification accuracy across all respiratory conditions while achieving better energy efficiency, verifying the system's suitability for real-world clinical applications.
\end{itemize}

The paper is structured as follows: Section \ref{sec:relatedwork} discusses previous studies on the classification of respiratory diseases. Section \ref{sec:materialMethods} provides detailed information on the methods, algorithms, and models for classifying respiratory diseases. The presentation of results and performance evaluation of the algorithms is detailed in Section \ref{sec:experimentsResults}. Finally, Section \ref{sec:conclusion} summarizes the key points from the previous sections and presents important conclusions, highlighting potential future developments.
