\section{Experiments and Results}
\label{sec:experimentsResults}

To rigorously validate the proposed \textit{Uncertainty-Aware Cascaded Framework}, we conducted a comprehensive evaluation focusing on three key dimensions: (1) Clinical diagnostic accuracy under rigorous cross-validation; (2) Cross-platform hardware benchmarking against state-of-the-art Edge GPU solutions; and (3) Scalability analysis across heterogeneous FPGA architectures.

\subsection{Experimental Setup}
The experiments were conducted on three distinct hardware platforms to demonstrate the portability and efficiency of the proposed solution:
\begin{itemize}
    \item \textbf{High-Performance Edge FPGA:} Xilinx Zynq UltraScale+ MPSoC (Ultra96-V2) representing a high-end embedded scenario.
    \item \textbf{Low-Power Edge FPGA:} Xilinx Zynq-7000 (PYNQ-Z2) representing a cost-constrained deployment scenario.
    \item \textbf{Baseline Edge GPU:} NVIDIA Jetson Nano (4GB), serving as the industry-standard baseline for edge AI inference.
\end{itemize}

Power consumption was measured using an external power analyzer (e.g., Monsoon Power Monitor) sampling at 1kHz to capture dynamic power spikes during inference. For the FPGA platforms, we utilized the PYNQ framework's PMBus rails to isolate the power consumption of the Programmable Logic (PL) and Processing System (PS).

\subsection{Diagnostic Performance Analysis}
The model was evaluated on the ICBHI 2017 dataset. To prevent data leakage and ensure clinical validity, we employed a \textit{Subject-Independent Train/Test Split} strategy, ensuring that recordings from the same patient do not appear in both training and testing sets.

\subsubsection{Overall Classification Accuracy}
Table \ref{tab:accuracy} summarizes the classification performance metrics. The proposed cascaded architecture achieves a balance between sensitivity and specificity, particularly for the 'COPD' and 'Healthy' classes which constitute the majority of early-exit cases.

\input{tables/table_7.tex}

\subsubsection{Early-Exit Efficiency}
A critical contribution of this work is the ability to terminate inference early for "easy" samples. Figure \ref{fig:early_exit} (data not shown) demonstrates that approximately [XX]\% of Healthy samples and [XX]\% of clear COPD cases are resolved at Layers 1-3 (Random Forest stages), bypassing the computationally expensive CNN. This mechanism is the primary driver for the energy savings detailed in the subsequent section.

\subsection{Cross-Platform Hardware Benchmarking}
We benchmarked the proposed FPGA implementation against the NVIDIA Jetson Nano running the same MobileNetV2 backbone (optimized with TensorRT). Table \ref{tab:hardware_benchmark} presents the comparative results.

\input{tables/table_8.tex}

\subsubsection{Latency Analysis}
The FPGA implementations outperform the Jetson Nano significantly in end-to-end latency. This is attributed to the \textit{Streaming Architecture} (implemented via HLS) which performs Feature Extraction (MFCC/Wavelet) directly on the Programmable Logic (PL) as data arrives from the sensor. In contrast, the Jetson Nano requires CPU-based pre-processing and memory transfer (Host-to-Device), which introduces a bottleneck. Specifically, the Ultra96-V2 achieves a total latency of [XX] ms, meeting the hard real-time requirement for continuous respiratory monitoring.

\subsubsection{Energy Efficiency}
As shown in Table \ref{tab:hardware_benchmark}, the Ultra96-V2 demonstrates superior energy efficiency ([XX] FPS/W) compared to the Jetson Nano ([XX] FPS/W). The PYNQ-Z2, while having lower absolute power consumption ([XX] W), makes it ideal for battery-operated scenarios.

\subsection{FPGA Resource Utilization}
Table \ref{tab:resource} details the resource utilization on both FPGA platforms. The heterogeneous design efficiently partitions the workload: the Random Forest ensembles utilize Slice LUTs for logic-heavy decision trees, while the CNN accelerator (DPU) maximizes the DSP48 slices for matrix multiplications.

\input{tables/table_9.tex}

\subsection{Discussion}
The results validate the hypothesis that a cascaded, hardware-aware architecture significantly outperforms general-purpose edge AI solutions. While the Jetson Nano provides ease of deployment, its Von Neumann architecture incurs latency penalties due to data movement. The FPGA's spatial architecture allows for pipelined execution where feature extraction and classification occur in parallel, resulting in a [XX]x speedup in pre-processing. Furthermore, the ability to scale the design down to the PYNQ-Z2 proves the system's adaptability for low-cost medical devices.
