\section{Conclusion}
\label{sec:conclusion}
This study has designed and developed a hierarchical embedded system using respiratory sound features to diagnose respiratory diseases. The system was successfully deployed on the FPGA Ultra96V2, achieving the expected accuracy and performance. With a peak average accuracy of 94.94\% across a 3-fold cross-validation for three classes—Healthy, COPD, and Non-COPD—the model demonstrates the effectiveness and reliability of the proposed method in classifying respiratory conditions. The system exhibits superior parallel processing capabilities and flexibility, significantly reducing disease classification time. This advantage translates into faster processing speeds and reduced waiting times during the diagnostic process. Additionally, the QAT pipeline achieves minimal accuracy drop (from 97.98\% to 97.47\% on 198 samples) while reducing latency by 82.7\% on CPU tests compared to FP32, facilitating deployment on mobile or embedded devices and allowing for use in clinical and real-world settings.

The results of this research underscore the efficacy and broad application potential of the proposed method in diagnosing chronic obstructive pulmonary disease and other respiratory conditions. The hierarchical embedded system, designed with high accuracy, performance, and energy efficiency via structured distillation and hardware acceleration, paves the way for practical usage in supporting clinical diagnostic procedures and enhancing patient care quality.

\section*{Data Availability}
\addcontentsline{toc}{section}{Data Availability}
The ICBHI 2017 Respiratory Sound Database used in this study is publicly available.

% use section* for acknowledgment
\section*{Acknowledgment}
% addcontentsline needed when using bookmark hyperlinking, etc.
\addcontentsline{toc}{section}{Acknowledgment}
% enable scriptsize
%\scriptsize
The authors are grateful to the editor and the anonymous referees for their valuable comments, which significantly improved the results and presentation of this article. The research is supported by Posts and Telecommunications Institute of Technology, Vietnam.
